The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-08-26 sections/results.tex
Remove precip corrections and shrink offset range

Using WorldClim, NCEP/NCAR, ERA-Interim, CFSR (smoothed and original datasets) and NARR input climatologies (section~\ref{sec:climate}), PISM (section~\ref{sec:model}) was run using 0 to 15\degC  temperature offsets for 10~kyr to mimic glacial inception and the growth of the Cordilleran ice sheet towards its LGM configuration. Important differences in patterns of ice sheet growth, final glacial extent, and volume were attained (Fig. \ref{fig:cool06}-\ref{fig:best}).

@@

As illustrated in Figure \ref{fig:cool06}, spatial patterns and rates of ice sheet growth differ tremendously between the input climatologies, given a certain temperature depression. Because we performed a total of 8 simulations for each input climatology, we derived an ensemble of 96 simulations (Fig. \ref{fig:extent}). Despite temperature depressions as large as 15 °C to the input reference climatologies it is again visible that each leads to a different final ice sheet extent and volume (Fig. \ref{fig:extent} and \ref{fig:ivolarea}). Notably, for the smallest temperature offset value of 0\degC, NCAR and CFSR simulations lead to an ice-sheet, whereas WorldClim, NARR and ERA-Interim produce local ice caps only. In the case of WorldClim, ice is restricted to the Wrangell-St.~Elias mountains, an area presently glaciated. Several of the NCAR and CFSR simulations produce oversized ice sheets whose extent is primarily restricted by the domain boundaries. Differences in regional patterns can also be noted. For instance ERA-Interim ice sheets generally appear more northernly-centered than NARR ice sheets.

>>>>

Using WorldClim, NCEP/NCAR, ERA-Interim, CFSR (smoothed and original datasets) and NARR input climatologies (section~\ref{sec:climate}), PISM (section~\ref{sec:model}) was run using 0 to 10\degC  temperature offsets for 10~kyr to mimic glacial inception and the growth of the Cordilleran ice sheet towards its LGM configuration. Important differences in patterns of ice sheet growth, final glacial extent, and volume were attained (Fig. \ref{fig:cool06}-\ref{fig:best}).

@@

As illustrated in Figure \ref{fig:cool06}, spatial patterns and rates of ice sheet growth differ tremendously between the input climatologies, given a certain temperature depression. Because we performed a total of 11 simulations for each input climatology, we derived an ensemble of 66 simulations (Fig. \ref{fig:extent}). Despite temperature depressions as large as 10\degC to the input reference climatologies it is again visible that each leads to a different final ice sheet extent and volume (Fig. \ref{fig:extent} and \ref{fig:ivolarea}). Notably, for the smallest temperature offset value of 0\degC, NCAR and CFSR simulations lead to an ice-sheet, whereas WorldClim, NARR and ERA-Interim produce local ice caps only. In the case of WorldClim, ice is restricted to the Wrangell-St.~Elias mountains, an area presently glaciated. Several of the NCAR and CFSR simulations produce oversized ice sheets whose extent is primarily restricted by the domain boundaries. Differences in regional patterns can also be noted. For instance ERA-Interim ice sheets generally appear more northernly-centered than NARR ice sheets.
